%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-7pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-2pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://erickdolores.com/}{\Large Erick Dolores}} & Email: \href{mailto:edolore1@swarthmore.edu}{edolore1@swarthmore.edu}\\
  LinkedIn: \href{https://www.linkedin.com/in/erick-dolores/}{linkedin.com/in/erick-dolores/} & Mobile: 661-210-6739 \\
  Website: \href{http://erickdolores.com/}{erickdolores.com} & Github: \href{https://github.com/edolores}{github.com/edolores}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
    \resumeSubheading
      {Swarthmore College}{Swarthmore, PA}
      {B.S. in Computer Science \& B.A. in Educational Studies}{Aug 2018 -- May 2022(Expected)}

%-----------EXPERIENCE-----------------
\section{Experience}

    \resumeSubheading
      {Autodesk}{San Francisco, CA}
      {Software Engineer Intern}{May 2020 - Present}
      \resumeItemListStart
        \resumeItem{}
          {Implemented a Slack bot that will solve 90\% of customer support issues for the Forge Data team by automating how applications are onboarded into an internal eventing service.}
        \resumeItem{}
          {Utilized Python, AWS API Gateway, and AWS Lambda for hosting in order to provide high volume scalability while keeping usage inexpensive.}
        \resumeItem{}
          {Currently adding functionality to write user data into AWS Dynamo DB and AWS Kinesis and read application metrics from AWS CloudWatch.}
      \resumeItemListEnd

    \resumeSubheading
      {Google}{Remote}
      {SPS Participant}{Feb 2020 - May 2020}
      \resumeItemListStart
        \resumeItem{}
          {Developed an app that creates friend groups through a Tinder-like matching system in collaboration with a team of peers and a Google engineer by using Java, JavaScript, HTML, CSS, and Google services such as App Engine and Cloud Datastore.}
        \resumeItem{}
          {Contributed 1000+ lines of code to open source software using Git and GitHub, conducted code reviews with/for teammates, and extended new chat functionality to an existing codebase.}
      \resumeItemListEnd

    \resumeSubheading
      {Amtrak}{Philadelphia, PA}
      {Software Engineer Intern}{Jan 2020 - Apr 2020}
      \resumeItemListStart
        \resumeItem{}
          {Designed and documented the architecture for a Java-based web client that will use the SOAP protocol to accelerate the retrieval of SQL transaction logs from HP NonStop servers by 98\%.}
        \resumeItem{}
          {Reduced technical debt for a train scheduling app by writing Java code to introduce compatibility with new routes and using MySQL Workbench to create over a dozen SQL schemas.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Electronic Arts}{Redwood City, CA}
      {Software Engineer Intern}{May 2019 - Aug 2019}
      \resumeItemListStart
        \resumeItem{}
          {Practiced the Agile/Scrum development methodology to develop, stage, and produce a Grafana dashboard that extracts health data from Maxis Studio's live service infrastructure through API, JSON, and .INI file configurations.}
        \resumeItem{}
          {Imported metrics from services like Apache Cassandra, Redis, Jenkins, etc. using Graphite in order to monitor 20+ operations that helped with tasks like server migration to AWS cloud.}
        \resumeItem{}
          {Spun up AWS S3 instances, SQS messages, RDS connections, etc. in 4 different distributed system architectures to assure the functionality of a local test dashboard running off of a Docker container.}
      \resumeItemListEnd



%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Concurrent Web Server: }
      {A multithreaded HTTP server that can process multiple browser connections by using TCP sockets to transfer data, pthreads to parallelize functions, and Telnet/Wget to test the program.}
    \resumeSubItem{CLI File Downloader: }
      {This Java tool downloads files by using HTTP ranged requests to improve I/O performance, download speed, system resource usage, and scalability.}
    \resumeSubItem{DNS Client: }
      {An iterative DNS client written in Python that can pack, unpack, and parse binary data to
resolve domain host names (like google.com) to IP addresses.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
     \resumeSubItem{Languages: }
      {Java, C, C++, HTML, CSS, Javascript, Python, Spanish}
    \resumeSubItem{Technologies: }
      {Linux, Git/Github, Bitbucket, Maven, Valgrind, GDB, LaTex}
    \resumeSubItem{Coursework: }
      {Algorithms, Computer Networks, Operating Systems, Data Structures and Algorithms, Intro to Computer Systems}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
