%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {SPS Participant} % Job title
    {Google} % Organization
    {Remote Work} % Location
    {Jan. 2020 - May. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an app that creates friend groups through a Tinder-like matching system in collaboration with a team of peers and a Google engineer by using Java, JavaScript, HTML, CSS, and Google services such as App Engine and Cloud Datastore.}
        \item {Contributed 1000+ lines of code to open source software using Git and GitHub, conducted code reviews with/for teammates, and extended new chat functionality to an existing codebase.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Amtrak} % Organization
    {Philadelphia, Pennsylvania} % Location
    {Jan. 2020 - Apr. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and documented the architecture for a Java-based web client that will use the SOAP protocol to accelerate the retrieval of SQL transaction logs from HP NonStop servers by 98\%.}
        \item {Reduced technical debt for a train scheduling app by writing Java code to introduce compatibility with new routes and using MySQL Workbench to create over a dozen SQL schemas.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Intern} % Job title
    {Electronic Arts (EA)} % Organization
    {Redwood City, California} % Location
    {May. 2019 - Aug. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Practiced the Agile/Scrum development methodology to develop, stage, and produce a Grafana dashboard that extracts health data from Maxis Studio's live service infrastructure through API, JSON, and .INI file configurations.}
        \item {Imported metrics from services like Apache Cassandra, Redis, Jenkins, etc. using Graphite in order to monitor 20+ operations that helped with tasks like server migration to AWS cloud.}
        \item {Spun up AWS S3 instances, SQS messages, RDS connections, etc. in 4 different distributed system architectures to assure the functionality of a local test dashboard running off of a Docker container.}
      \end{cvitems}
    }

\end{cventries}
