%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {C, HTTP, TCP} % Job title
    {Concurrent Web Server} % Organization
    {Swarthmore College} % Location
    {February 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a multithreaded HTTP server that can process multiple browser connections by using TCP sockets to transfer data, pthreads to parallelize functions, and Telnet/Wget to test the program.}
        \item {Learned how to process an HTTP query and return text and binary file formats in an HTTP response, while using HTML to return either local files or 404 error codes.} 
        \item{Utilized GDB while unit testing helper functions in order to reverse engineer bugs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Python, DNS, UDP} % Job title
    {DNS Client} % Organization
    {Swarthmore College} % Location
    {November 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created an iterative DNS client that can pack, unpack, and parse binary data to resolve domain host names (like google.com) to IP addresses.}
        \item {Built the client on top of UDP sockets to send/receive data to root, TLD, and authoritative DNS servers.}
        \item{Made use of Wireshark to debug DNS response packets at the binary level.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Java, HTTP} % Job title
    {CLI File Downloader} % Organization
    {Swarthmore College} % Location
    {September 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Given a number of threads and a URL, this tool downloads files by using HTTP ranged requests to improve I/O performance, download speed, system resource usage, and scalability.}
        \item {Employing parallelization and object-oriented programming, the tool concurrently writes data from threads into .part files, which are combined and transferred to a single file channel.}
      \end{cvitems}
    }

\end{cventries}